The Clinicopathological Features and Survival Outcomes of Patients with Different Metastatic Sites in Stage IV Endometrial Cancer:A SEER-Based Cohort Study

### 2025-02-09 products/manuscript/Manuscript.qmd
Added more description based on Dr. @adreashandel comments. V2 #1

## General Background Information
_Provide enough background on your topic that others can understand the why and how of your analysis_ 
Endometrial cancer, a neoplasm originating from the endometrial lining, is the most common gynecological cancer in the United States.[@Monk2022] According to American Cancer Society 2024 statistics the incidence of uterine cancer is 67, 880 with 13,250 deaths. Due to its early symptomatic presentation, 70% of cases are diagnosed at stage I, where the five-year survival rate exceeds 90%. However, around 13% of patients are diagnosed at advanced stages (III/IV).

>>>>

## General Background Information
_Provide enough background on your topic that others can understand the why and how of your analysis_ 
Endometrial cancer, a neoplasm originating from the endometrial lining, is the most common gynecological cancer in the United States. According to American Cancer Society 2024 statistics the incidence of uterine cancer is 67, 880 with 13,250 deaths. Due to its early symptomatic presentation, 70% of cases are diagnosed at stage I, where the five-year survival rate exceeds 90%. However, around 13% of patients are diagnosed at advanced stages (III/IV).
